Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
Fixed first paragraph of rw

In this section, we motivate our work using three fields: PIM, data integration, and end-user mashups and toolkits.  Our primary motivation stems from field studies in PIM, where consolidating and working with data from multiple sources has remained a challenge for over a decade. Enabling PIM tools to support ad-hoc data integration has remained difficult because of the complex, theoretically difficult nature of data heterogeneity; specifically, reconciling the differences that arise among representations when data is created by different people, at different times, for different purposes. As described by Alon Halvey:

@@

Recently, users are experiencing data fragmentation~\cite{Jones05towardsa} across multiple web-based applications and services, and struggle to consolidate across them~\cite{bergman,boardmansasse}.  In our own previously-conducted field study, (reference anonymised) we observed variations of manual ``coping strategies'' (or, if programmers, elaborate, custom-coded one-off solutions) to allow people to manage both online and offline data.  Similar findings from other studies include Voida et al.'s observations of volunteer coordinators' ``homebrew databases'', manually-maintained information assemblages concocted to handle the widely varied and heterogeneous data collection requirements such groups needed to coordinate their activities \cite{Voida:2011:HDC:1978942.1979078}.

A number of research PIM systems have demonstrated a great number of ways that users could benefit from better support for data integration.  For example, SEMEX's \cite{semex} rich uniform query interface allowed users to quickly trace references of people, places and things across files, folders and repositories.  Similarly, Haystack, a personal information platform, allowed users to visualise and customise how they worked with their data in a uniform, consolidated manner \cite{haystack}. Pertaining to each system's ability to integrate information from arbitrary new data sources, however, both systems generally required new sources to either already conform to a pre-specified set of ontologies, or have the user provide a manual specify such a mapping translation themselves.

>>>>

In this section, we motivate our work using three fields: PIM, data integration, and end-user mashups and toolkits.  Our primary motivation stems from field studies in PIM, which foregrounded work to consolidate data from multiple sources and this still remains a challenge.  Specifically, reconciling the differences that arise among representations when data is created by different people, at different times, for different purposes. As described by Alon Halevy:

@@

A result of this problem is that users can experience data fragmentation~\cite{Jones05towardsa} across multiple web-based applications and services, and struggle to consolidate across them~\cite{bergman,boardmansasse}.  In our own previously-conducted field study, (reference anonymised) we observed variations of manual ``coping strategies'' (or, if programmers, elaborate, custom-coded one-off solutions) to allow people to manage both online and offline data.  Similar findings from other studies observed volunteers' ``homebrew databases'': manually-maintained information collated to handle the heterogeneous data requirements of groups needing to coordinate their activities~\cite{Voida:2011:HDC:1978942.1979078}.\looseness=-1

A number of research PIM systems have demonstrated numerous ways that users cab benefit from better data integration support.  For example, SEMEX's \cite{semex} rich uniform query interface allowed users to quickly trace references of people, places and things across files, folders and repositories.  Similarly, Haystack, a personal information platform, allowed users to visualise and customise how they worked with their data in a uniform, consolidated manner \cite{haystack}. Pertaining to each system's ability to integrate information from arbitrary new data sources, however, both systems generally required new sources to either already conform to a pre-specified set of ontologies, or have the user provide a manual specify such a mapping translation themselves.
